Concurrent, Parallel Garbage Collection in Linear Time

### 2016-05-27 finaletd/mainabstract.tex
abastractg

The uncertainty in the order of operations makes manual memory management of concurrent programs difficult. Some programming lanugages offer incomplete garbage collection feature for concurrent programming like smart pointers in C++.
%Languages like C++ offer support for memory management using using smart pointers.
Smart pointers can collect all garbage only if developer identifies cycles being created in the object graph. With uncertainty in the order of operations in the concurrent programs, the cycle creation cannot be detected unless the entire object graph can be traversed by the process/thread.
 Smart pointer usage does not guarantee protection from memory leaks unless cycle can be detected as process/thread mutating reference graph.
 % For cyclic object graphs, a concurrent process must identify that it is creating a cycle and must use a special type of smart pointer to close a cyclic. Smart pointers, therefore, require hints from the programmer to avoid memory leaks. 
 General garbage collectors, on the other hand, can avoid memory leaks, dangling pointers, and double deletion problems in any programming environment without help from the programmer.

Concurrent programming comes in two flavors : shared memory and distributed memory. Shared memory systems help threads to communicate with each other through shared memory. Most shared memory systems contain single garbage collector that runs concurrently. In distributed memory system, multiple systems contain the process that communicates through messages sent across a network. These systems require synchronization barrier among all the garbage collector in each system to solve the problem. Our thesis focuses on designing garbage collection algorithms for each environment that takes advantage of the environment.

>>>>

The uncertainty in the order of operations makes manual memory management of concurrent programs difficult. Some programming lanugages offer unfriendlyollection feature for concurrent programming like smart pointers in C++.
%Languages like C++ offer support for memory management using using smart pointers.
Smart pointers can collect all garbage only if developer identifies cycles being created in the reference graph. With uncertainty in the order of operations in the concurrent programs, the cycle creation cannot be detected unless the entire reference graph can be traversed by the process/thread.
Smart pointer usage does not guarantee protection from memory leaks unless cycle can be detected as process/thread create them. Detecting cycle as they are being created is very expensive.
% For cyclic object graphs, a concurrent process must identify that it is creating a cycle and must use a special type of smart pointer to close a cyclic. Smart pointers, therefore, require hints from the programmer to avoid memory leaks. 
General garbage collectors, on the other hand, can avoid memory leaks, dangling pointers, and double deletion problems in any programming environment without help from the programmer.

Concurrent programming comes in two flavors : shared memory and distributed memory. Shared memory systems help threads to communicate with each other through . Most shared memory systems contain single garbage collector that runs concurrently. In distributed memory system, multiple systems contain the process that communicates through messages sent across a networks These systems require synchronization barrier among all the garbage collector in each system to solve the problem. Our thesis focuses on designing garbage collection algorithms for each environment that takes advantage of the environment.
